---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Clark Sims

<!-- badges: start -->
<!-- badges: end -->

# Currently
**Senior Data Analyst** 

First Electric Cooperative Corporation

# Previously
**Staff Scientist/Senior Research Associate/Postdoctoral Fellow**

Arkansas Children's Nutrition Center + University of Arkansas for Medical Sciences

# Education
**PhD**

University of Arkansas for Medical Sciences
Pharmacology

**BA**

Hendrix College
Chemistry





```{r exit, include = FALSE}
knitr::knit_exit()
```
You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/v1/examples>.

```{r render, include = FALSE}
devtools::build_readme()
```
